---
title: "pairwise_viz_updated"
output: html_document
---

```{r}
library(tidyverse)

```


# BLUE


```{r}
#blue_sigs <- readRDS("/Volumes/databuddy/Variability/data/Blue_all_sigs_updated.rda")

#blue_lands <- data.frame(scan_id = unique(blue_sigs$scan_id))

#blue_lands <- blue_lands %>% mutate(scan = scan_id) %>% separate(scan, into = c("barrel", "land", "bullet", "operator", "machine", "round"), sep = "-")

#write_csv(blue_lands, "../data/variability_scans/blue_gt_update.csv")

blue <- readRDS("/Volumes/databuddy/Variability/data/blue_pairwise_all.rda")
blue <- blue %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")

blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         machine_S2 == "Sneox1", operator_S2 == "Anyesha", 
         round_S2 == "Round 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~bullet_S2 + round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

```

## Anyesha
```{r}
# bullet 1
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Anyesha", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Anyesha", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Anyesha", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


## Marco
```{r}
# bullet 1
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Marco", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Marco", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Marco", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

## Mark
```{r}
# bullet 1
blue %>%
    filter(barrel_S1 == "Barrel Blue", barrel_S2 == "Barrel Blue") %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Mark", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
blue %>%
    filter(barrel_S1 == "Barrel Blue", barrel_S2 == "Barrel Blue") %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Mark", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
blue %>%
  filter(barrel_S1 == "Barrel Blue", barrel_S2 == "Barrel Blue") %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Mark", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land_S1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20)) + 
  labs(title = "Barrel Blue - Bullet 3 - Operator F", subtitle =  "base: Barrel Blue - Bullet 1 - Operator B - Sneox1 - Round 1", 
       x = "Operator F Scans", y = "Base Scans") + 
  theme(plot.subtitle = element_text(face = "italic"))
```


## Mya
```{r}
# bullet 1
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Mya", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20)) + 
  labs(title = "Barrel Blue - Bullet 1 - Mya", subtitle =  "base: Barrel Blue - Bullet 1 - Anyesha - Sneox1 - Round 1") + 
  theme(plot.subtitle = element_text(face = "italic"))



mya_b1_issues <- readRDS("../data/variability_scans/issues/mya_blue_scans.rda")
image_x3p(mya_b1_issues$x3p[[1]]) 
image_x3p(mya_b1_issues$x3p[[2]])
image_x3p(mya_b1_issues$x3p[[3]])
image_x3p(mya_b1_issues$x3p[[4]])
image_x3p(mya_b1_issues$x3p[[5]])
image_x3p(mya_b1_issues$x3p[[6]])


# bullet 2
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Mya", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Mya", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

## Samantha
```{r}
# bullet 1
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Samantha", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Samantha", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
blue %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Samantha", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "steelblue", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


# ORANGE 
First, add sets of signatures to old GT file!  

```{r}
orange_sigs <- readRDS("/Volumes/databuddy/Variability/data/Orange_all_sigs_updated.rda")
orange_gt_1 <- read_csv("../data/variability_scans/orange_gt.csv")

orange_lands <- data.frame(scan_id = unique(orange_sigs$scan_id))

orange_lands <- orange_lands %>% mutate(scan = scan_id) %>% separate(scan, into = c("barrel", "land", "bullet", "operator", "machine", "round"), sep = "-")

orange_lands <- left_join(orange_lands, orange_gt_1)

write_csv(orange_lands, "../data/variability_scans/orange_gt_update.csv")

```

Now, read in and split into S1, S2 elements!
```{r}
orange <- readRDS("/Volumes/databuddy/Variability/data/orange_pairwise_all.rda")
orange <- orange %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")

orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         machine_S2 == "Sneox1", operator_S2 == "Anyesha", 
         round_S2 == "Round 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~bullet_S2 + round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

## Anyesha
```{r}
# bullet 1
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Anyesha", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Anyesha", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Anyesha", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```




## Marco
```{r}
# bullet 1
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Marco", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Marco", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Marco", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```



## Mark
```{r}
# bullet 1
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Mark", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Mark", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Mark", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


## Samantha
```{r}
# bullet 1
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Samantha", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
orange %>%
  filter(bullet_S1 == "Bullet 1", machine_S1 == "Sneox1", 
         operator_S1 == "Anyesha", round_S1 == "Round 1", 
         operator_S2 == "Samantha", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
orange %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Carley", round_S1 == "Round 1", 
         operator_S2 == "Samantha", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

# PINK
First, add sets of signatures to old GT file!  

```{r}
pink_sigs <- readRDS("/Volumes/databuddy/Variability/data/Pink_all_sigs_updated.rda")
pink_gt_1 <- read_csv("../data/variability_scans/pink_gt.csv")

pink_lands <- data.frame(scan_id = unique(pink_sigs$scan_id))

pink_lands <- pink_lands %>% mutate(scan = scan_id) %>% separate(scan, into = c("barrel", "land", "bullet", "operator", "machine", "round"), sep = "-")

pink_lands <- left_join(pink_lands, pink_gt_1)

write_csv(pink_lands, "../data/variability_scans/pink_gt_update.csv")

```

Now, read in and split into S1, S2 elements!
```{r}
pink <- readRDS("/Volumes/databuddy/Variability/data/pink_pairwise_all.rda")
pink <- pink %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")

pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         machine_S2 == "Sneox1", operator_S2 == "Anyesha", 
         round_S2 == "Round 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~bullet_S2 + round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

## Anyesha
```{r}
# bullet 1
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Anyesha", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Anyesha", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Anyesha", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```




## Marco
```{r}
# bullet 1
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Marco", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Marco", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Marco", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```



## Mark
```{r}
# bullet 1
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Mark", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Mark", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Mark", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


## Samantha
```{r}
# bullet 1
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Samantha", bullet_S2 == "Bullet 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))



# bullet 2
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Samantha", bullet_S2 == "Bullet 2") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

# bullet 3
pink %>%
  filter(bullet_S1 == "Bullet 3", machine_S1 == "Sneox1", 
         operator_S1 == "Allison", round_S1 == "Round 1", 
         operator_S2 == "Samantha", bullet_S2 == "Bullet 3") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "salmon", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```



# Visualize pairwise score distributions  

```{r}
orange %>% 
  ggplot() + 
  geom_histogram(aes(x = rfscore), color = "white", fill = "darkorange") + 
  geom_histogram(aes(x = ccf), color = "black", fill = NA) + 
  theme_bw() 

pink %>% 
  ggplot() + 
  geom_histogram(aes(x = rfscore), color = "white", fill = "salmon") + 
  geom_histogram(aes(x = ccf), color = "black", fill = NA) + 
  theme_bw()

blue %>% 
  ggplot() + 
  geom_histogram(aes(x = rfscore), color = "white", fill = "steelblue") + 
  geom_histogram(aes(x = ccf), color = "black", fill = NA) + 
  theme_bw() 


```


# Ground Truthing  

Step 1. Create list of all lands / scans and save as CSV.  
Step 2. Left join the list of all of them with the list of already ID'd ground truth from Phase 1. 
Step 3. Ground truth remaining lands

```{r}
orange_sigs <- readRDS("../data/variability_scans/Orange_all_sigs_updated.rda")
orange_gt_1 <- read_csv("../data/variability_scans/orange_gt.csv")

orange_lands <- data.frame(scan_id = unique(orange_sigs$scan_id))

orange_lands <- orange_lands %>% mutate(scan = scan_id) %>% separate(scan, into = c("barrel", "land", "bullet", "operator", "machine", "round"), sep = "-")

orange_lands <- left_join(orange_lands, orange_gt_1)

write_csv(orange_lands, "../data/variability_scans/orange_gt_update.csv")
```

```{r}
pink_sigs <- readRDS("../data/variability_scans/Pink_all_sigs_updated.rda")
pink_gt_1 <- read_csv("../data/variability_scans/pink_gt.csv")

pink_lands <- data.frame(scan_id = unique(pink_sigs$scan_id))

pink_lands <- pink_lands %>% mutate(scan = scan_id) %>% separate(scan, into = c("barrel", "land", "bullet", "operator", "machine", "round"), sep = "-")

pink_lands <- left_join(pink_lands, pink_gt_1)

write_csv(pink_lands, "../data/variability_scans/pink_gt_update.csv")
pink_lands %>% group_by(operator, bullet, machine, round) %>% summarise(n = n())
```



