---
title: "establishing ground truth via pairwise"
output: html_document
---

## SCORE VIZ FOR ESTABLISHING GROUND TRUTH  

# ORANGE 

```{r}
orange_sigs <- readRDS("../data/variability_scans/Orange_all_sigs_updated.rda")

orange_lands <- data.frame(scan_id = unique(orange_sigs$scan_id))

orange_lands <- orange_lands %>% mutate(scan = scan_id) %>% separate(scan, into = c("barrel", "land", "bullet", "operator", "machine", "round"), sep = "-")

#write_csv(orange_lands, "../data/variability_scans/orange_gt.csv")
```

```{r}
rfscores_orange_b123 <- readRDS("../data/variability_scans/orange_b123_rfscores.rda")
rfscores_orange_b123 <- rfscores_orange_b123 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")

rfscores_orange_b123 %>%
  filter(bullet_S1 == "Bullet 1" & machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~bullet_S2 + round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

```{r}
rfscores_orange_b1 <- readRDS("../data/variability_scans/orange_b1_rfscores.rda")
rfscores_orange_b1 <- rfscores_orange_b1 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")
```

The base land is "Connor - Bullet 1 - Sneox1 - Round 1 - LAND 1"

## BULLET 1  
### ALLISON

```{r, echo = F, warning = F, message = F}
rfscores_orange_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### ANYESHA

```{r, echo = F, warning = F, message = F}
rfscores_orange_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Anyesha") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


### CARLEY

```{r, echo = F, warning = F, message = F}
rfscores_orange_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Carley") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### CONNOR

```{r, echo = F, warning = F, message = F}
rfscores_orange_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Connor") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### MYA

```{r, echo = F, warning = F, message = F}
rfscores_orange_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Mya") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```





## BULLET 2 

```{r}
rfscores_orange_b2 <- readRDS("../data/variability_scans/orange_b2_rfscores.rda")
rfscores_orange_b2 <- rfscores_orange_b2 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")
```


### ALLISON

```{r, echo = F, warning = F, message = F}
rfscores_orange_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### ANYESHA

```{r, echo = F, warning = F, message = F}
rfscores_orange_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Anyesha") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


### CARLEY

```{r, echo = F, warning = F, message = F}
rfscores_orange_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Carley") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### CONNOR

```{r, echo = F, warning = F, message = F}
rfscores_orange_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Connor") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### MYA

```{r, echo = F, warning = F, message = F}
rfscores_orange_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Mya") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


## BULLET 3 

```{r}
rfscores_orange_b3 <- readRDS("../data/variability_scans/orange_b3_rfscores.rda")
rfscores_orange_b3 <- rfscores_orange_b3 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")
```


### ALLISON

```{r, echo = F, warning = F, message = F}
rfscores_orange_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### ANYESHA

```{r, echo = F, warning = F, message = F}
rfscores_orange_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Anyesha") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


### CARLEY

```{r, echo = F, warning = F, message = F}
rfscores_orange_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Carley") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### CONNOR

```{r, echo = F, warning = F, message = F}
rfscores_orange_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Connor") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### MYA

```{r, echo = F, warning = F, message = F}
rfscores_orange_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Mya") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```











# GREEN 

```{r}
green_sigs <- readRDS("../data/variability_scans/Green_all_sigs.rda")

green_lands <- data.frame(scan_id = unique(green_sigs$scan_id))

green_lands <- green_lands %>% mutate(scan = scan_id) %>% separate(scan, into = c("barrel", "land", "bullet", "operator", "machine", "round"), sep = "-")

#write_csv(green_lands, "../data/variability_scans/green_gt.csv")
```

```{r}
rfscores_green_b123 <- readRDS("../data/variability_scans/green_b123_rfscores.rda")
rfscores_green_b123 <- rfscores_green_b123 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")

rfscores_green_b123 %>%
  filter(bullet_S1 == "Bullet 1" & machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~bullet_S2 + round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


## BULLET 1  

```{r}
rfscores_green_b1 <- readRDS("../data/variability_scans/green_b1_rfscores.rda")
rfscores_green_b1 <- rfscores_green_b1 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")
```


### ALLISON

```{r, echo = F, warning = F, message = F}
rfscores_green_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### ANYESHA

```{r, echo = F, warning = F, message = F}
rfscores_green_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Anyesha") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


### CARLEY

```{r, echo = F, warning = F, message = F}
rfscores_green_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Carley") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### CONNOR

```{r, echo = F, warning = F, message = F}
rfscores_green_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Connor") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### MYA

```{r, echo = F, warning = F, message = F}
rfscores_green_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Mya") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```








## BULLET 2 

```{r}
rfscores_green_b2 <- readRDS("../data/variability_scans/green_b2_rfscores.rda")
rfscores_green_b2 <- rfscores_green_b2 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")
```


### ALLISON

```{r, echo = F, warning = F, message = F}
rfscores_green_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### ANYESHA

```{r, echo = F, warning = F, message = F}
rfscores_green_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Anyesha") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


### CARLEY

```{r, echo = F, warning = F, message = F}
rfscores_green_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Carley") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### CONNOR

```{r, echo = F, warning = F, message = F}
rfscores_green_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Connor") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### MYA

```{r, echo = F, warning = F, message = F}
rfscores_green_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Mya") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```








## BULLET 3 

```{r}
rfscores_green_b3 <- readRDS("../data/variability_scans/green_b3_rfscores.rda")
rfscores_green_b3 <- rfscores_green_b3 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")
```


### ALLISON

```{r, echo = F, warning = F, message = F}
rfscores_green_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### ANYESHA

```{r, echo = F, warning = F, message = F}
rfscores_green_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Anyesha") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


### CARLEY

```{r, echo = F, warning = F, message = F}
rfscores_green_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Carley") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### CONNOR

```{r, echo = F, warning = F, message = F}
rfscores_green_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Connor") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### MYA

```{r, echo = F, warning = F, message = F}
rfscores_green_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Mya") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```




# PINK 

```{r}
pink_sigs <- readRDS("../data/variability_scans/Pink_all_sigs.rda")

pink_lands <- data.frame(scan_id = unique(pink_sigs$scan_id))

pink_lands <- pink_lands %>% mutate(scan = scan_id) %>% separate(scan, into = c("barrel", "land", "bullet", "operator", "machine", "round"), sep = "-")

#write_csv(pink_lands, "../data/variability_scans/pink_gt.csv")
```

```{r}
rfscores_pink_b123 <- readRDS("../data/variability_scans/pink_b123_rfscores.rda")
rfscores_pink_b123 <- rfscores_pink_b123 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")

rfscores_pink_b123 %>%
  filter(bullet_S1 == "Bullet 1" & machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~bullet_S2 + round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


## BULLET 1

```{r}
rfscores_pink_b1 <- readRDS("../data/variability_scans/pink_b1_rfscores.rda")
rfscores_pink_b1 <- rfscores_pink_b1 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")
```


### ALLISON

```{r, echo = F, warning = F, message = F}
rfscores_pink_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### ANYESHA

```{r, echo = F, warning = F, message = F}
rfscores_pink_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Anyesha") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


### CARLEY

```{r, echo = F, warning = F, message = F}
rfscores_pink_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Carley") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### CONNOR

```{r, echo = F, warning = F, message = F}
rfscores_pink_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Connor") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### MYA

```{r, echo = F, warning = F, message = F}
rfscores_pink_b1 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Mya") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


## BULLET 2

```{r}
rfscores_pink_b2 <- readRDS("../data/variability_scans/pink_b2_rfscores.rda")
rfscores_pink_b2 <- rfscores_pink_b2 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")
```


### ALLISON

```{r, echo = F, warning = F, message = F}
rfscores_pink_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### ANYESHA

```{r, echo = F, warning = F, message = F}
rfscores_pink_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Anyesha") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


### CARLEY

```{r, echo = F, warning = F, message = F}
rfscores_pink_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Carley") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### CONNOR

```{r, echo = F, warning = F, message = F}
rfscores_pink_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Connor") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### MYA

```{r, echo = F, warning = F, message = F}
rfscores_pink_b2 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Mya") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

## BULLET 3

```{r}
rfscores_pink_b3 <- readRDS("../data/variability_scans/pink_b3_rfscores.rda")
rfscores_pink_b3 <- rfscores_pink_b3 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")
```


### ALLISON

```{r, echo = F, warning = F, message = F}
rfscores_pink_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### ANYESHA

```{r, echo = F, warning = F, message = F}
rfscores_pink_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Anyesha") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


### CARLEY

```{r, echo = F, warning = F, message = F}
rfscores_pink_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Carley") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### CONNOR

```{r, echo = F, warning = F, message = F}
rfscores_pink_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Connor") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

### MYA

```{r, echo = F, warning = F, message = F}
rfscores_pink_b3 %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Mya") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```













