---
title: "function to make a pairing ID"
output: html_document
---
First, read in the packages.  

```{r packages, echo = F, warning = F, message = F}
library(tidyverse)
library(bulletxtrctr)
library(x3ptools)
library(gridExtra)
library(randomForest)
```


I want to do two things: 

(1) Make a function and see if I can get the right things to work for the "beginning" of the pairwise comparisons pipeline.
(2) Look at already calculated RF scores, apply it, and see whether RF scores for pairs with the same "pairing_ID" are equivalent. 


## Step 1: Make the function and test using the orange_sigs.  

Input should be a vector of scan_ids.

```{r}
orange_sigs <- readRDS("../data/variability_scans/orange_123_sigs.rda")
orange_lands <- unique(orange_sigs$scan_id) 

make_comparison_grid <- function(scan_ids, self_comparisons = T){
  combos <- combn(scan_ids, 2) %>% t()
  combos_df <- data.frame(land1 = combos[,1], land2 = combos[,2]) 
  if(self_comparisons == T){
    self_combos <- data.frame(land1 = scan_ids, land2 = scan_ids)
    combos_df <- rbind(combos_df, self_combos) %>%
      mutate(pairing_id = paste0(land1, "_", land2))
  }
  else(combos_df <- combos_df %>% 
         mutate(pairing_id = paste0(land1, "_", land2)))
  return(combos_df)
}

check_orange_grid <- make_comparison_grid(scan_ids = orange_lands)


```

Things are looking good! 

Now let's see if randomForest scores are "symmetric" for comparisons of the same signatures. We'll test with the scores for Barrel Orange, Bullet 1. 

```{r}
orange_b1_scores <- readRDS("../data/variability_scans/orange_b1_rfscores.rda")

check_orange_grid <- check_orange_grid %>% mutate(land1 = as.character(land1), land2 = as.character(land2))
orange_b1_scores <- left_join(orange_b1_scores, check_orange_grid)

orange_b1_scores <- orange_b1_scores %>% mutate(pairing_id_alt = paste0(land2, "_", land1),
                            pairing_id_combo = ifelse(is.na(pairing_id), pairing_id_alt, pairing_id))

orange_b1_scores %>% 
  group_by(pairing_id_combo) %>% 
  summarise(sd(rfscore, na.rm = T))
```

It appears that when 2 combinations have the same "pairing ID" - essentially, they are the same comparison - the RFscores are the same. This is what we expect. 

Keep in mind we want to use this function as part of the R\&R pipeline, not for general comparison of two bullets. Once we already know the "ground truth" of what LEAs match what LEAs. 

I am curious about the whole "pairwise visuals" thing though... 

Things get a little weird though - so, you can still do visuals, if you're careful. But because visuals are in the lane of "land_S1", "land_S2" and all of those things, if you try to subset, you get weird things. Like, for example, when comparing Orange Bullet 1 if you subset to make "operator_S1" Connor, only Connor and Mya show up as operators in "S2" because of the order the combinations were grabbed. Allison, Anyesha, and Carley must be "operator_S1" for all of their comparisons with Connor's signatures. 

However, this shouldn't matter for the pairwise comparisons modeling, because we are using an indicator of "__ S1 == __ S2", so it doesn't matter which order they come in, just whether they are equivalent or not. 

```{r}
rfscores_orange_b1 <- rfscores_orange_b1 %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")


orange_b1_scores <- orange_b1_scores %>%
  mutate(id_S1 = land1, id_S2 = land2) %>%
  separate(col = id_S1, 
           into = c("barrel_S1", "land_S1", "bullet_S1", 
                    "operator_S1", "machine_S1", "round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("barrel_S2", "land_S2", "bullet_S2", 
                    "operator_S2", "machine_S2", "round_S2"), sep = "-")


## the "usual" visualization for the whole thing
orange_b1_scores %>%
  filter(operator_S1 == "Connor" & operator_S2 == "Allison") %>% 
  filter(round_S1 == "Round 1", machine_S1 == "Sneox1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~machine_S2 + round_S2, nrow = 1) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))

## the filtered viz for just comparisons that involve non-NA pairing_ids. 
orange_b1_scores %>%
  filter(!is.na(pairing_id)) %>%
  filter(operator_S1 == "Connor", machine_S1 == "Sneox1", round_S1 == "Round 1") %>% 
  ggplot(aes(x = land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~operator_S2 + machine_S2 + round_S2, nrow = 2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```




