---
title: "user-meas pairwise models"
output: html_document
---

```{r packages, echo = F, warning = F, message = F}
library(tidyverse)
library(gridExtra)
library(lme4)
library(bulletxtrctr)
```


First, we want to add our "unique_id" for each land to the signature data, so we can group them by that and align the lands. 
```{r}
user_sigs <- readRDS("../data/user_meas_sigs.rda")
head(user_sigs)
user_sigs <- user_sigs %>% 
  select(-barrellandbullet, -barrelland) %>% 
  select(scan_id, sigs)
head(user_sigs)

user_gt <- read_csv("../data/user_gt.csv")
user_sigs <- full_join(user_sigs, user_gt)

user_sigs <- user_sigs %>% filter(Round != "Round 0")

user_bullet_gt <- read_csv("../data/user_bullets_gt.csv")
user_sigs <- left_join(user_sigs, user_bullet_gt)

user_ops <- read_csv("../data/user_operators_blind.csv")
user_sigs <- left_join(user_sigs, user_ops)
```


## BARREL 6 VIZ OF SIGNATURES  

```{r}
barrel6land1 <- user_sigs %>% filter(unique_id == "BL 6-1")
barrel6land1 <- barrel6land1 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel6land1$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))

b6l1_long <- barrel6land1 %>% unnest(sigs_aligned)

b6l1_long %>% ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code))) + 
  geom_line(aes(x = x_aligned, y = sig1)) + 
  theme_bw() 

barrel6land2 <- user_sigs %>% filter(unique_id == "BL 6-2")
#head(barrel6land2)
barrel6land2 <- barrel6land2 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel6land2$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))


barrel6land3 <- user_sigs %>% filter(unique_id == "BL 6-3")
barrel6land3 <- barrel6land3 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel6land3$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))

barrel6land4 <- user_sigs %>% filter(unique_id == "BL 6-4")
barrel6land4 <- barrel6land4 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel6land4$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))

barrel6land5 <- user_sigs %>% filter(unique_id == "BL 6-5")
barrel6land5 <- barrel6land5 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel6land5$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))

barrel6land6 <- user_sigs %>% filter(unique_id == "BL 6-6")
barrel6land6 <- barrel6land6 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel6land6$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))

```


```{r, echo = F, warning = F, message = F}
barrel6 <- rbind(barrel6land1, barrel6land2, barrel6land3, barrel6land4, barrel6land5, barrel6land6)
saveRDS(barrel6, "../data/user_aligned_sigs.rda")

b6_long <- barrel6 %>% unnest(sigs_aligned)
head(b6_long)


b6_long %>% 
  #filter( unique_id == "BL 6-5") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = sig1), alpha = 0.8) + 
  theme_bw() + 
  facet_wrap(~unique_id, nrow = 2) + 
  labs(title = "Hamby set Barrel 6")


b6_long %>% ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = sig1), alpha = 0.8) + 
  theme_bw() + 
  facet_grid(operator_code~unique_id) + 
  labs(title = "Hamby set Barrel 6")


b6_long %>% ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(Machine)), alpha = 0.8) + 
  geom_line(aes(x = x_aligned, y = sig1), alpha = 0.8) + 
  theme_bw() + 
  facet_grid(operator_code~unique_id) + 
  labs(title = "Hamby set Barrel 6")

```


```{r}
b6_long %>% 
  filter( unique_id == "BL 6-5") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(Round)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = sig1), alpha = 0.8) + 
  theme_bw() + 
  facet_grid(Operator~bullet_code) + 
  labs(title = "Hamby set Barrel 6") 
```



I now want to calculate an average signature height for each $x$ location $m$ for each barrel-land signature, and look at the patterns of error from that mean.  
```{r}
sig_errors <- b6_long %>%
  group_by(unique_id, x_aligned) %>%
  mutate(mean_sig = mean(sig2, na.rm = T), 
         sig_error = sig2 - mean_sig) %>%
  ungroup()

mean_plot_65 <- sig_errors %>% 
  filter( unique_id == "BL 6-5") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 5") + 
  scale_color_discrete(name = "")

error_plot_65 <- sig_errors %>%
  filter( unique_id == "BL 6-5") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(operator_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "")

grid.arrange(mean_plot_65, error_plot_65, nrow = 2)

```


Let's look at each of them for Barrel 6!  
```{r}
mean_plot_61 <- sig_errors %>% 
  filter( unique_id == "BL 6-1") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 1") + 
  scale_color_discrete(name = "Operator")

error_plot_61 <- sig_errors %>%
  filter( unique_id == "BL 6-1") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(operator_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Operator")
  
mean_plot_62 <- sig_errors %>% 
  filter( unique_id == "BL 6-2") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 2") + 
  scale_color_discrete(name = "Operator")

error_plot_62 <- sig_errors %>%
  filter( unique_id == "BL 6-2") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(operator_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Operator")


mean_plot_63 <- sig_errors %>% 
  filter( unique_id == "BL 6-3") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 3") + 
  scale_color_discrete(name = "Operator")

error_plot_63 <- sig_errors %>%
  filter( unique_id == "BL 6-3") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(operator_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Operator")


mean_plot_64 <- sig_errors %>% 
  filter( unique_id == "BL 6-4") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 4") + 
  scale_color_discrete(name = "Operator")

error_plot_64 <- sig_errors %>%
  filter( unique_id == "BL 6-4") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(operator_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Operator")

mean_plot_65 <- sig_errors %>% 
  filter( unique_id == "BL 6-5") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 5") + 
  scale_color_discrete(name = "Operator")

error_plot_65 <- sig_errors %>%
  filter( unique_id == "BL 6-5") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(operator_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Operator")

mean_plot_66 <- sig_errors %>% 
  filter( unique_id == "BL 6-6") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(operator_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 6") + 
  scale_color_discrete(name = "Operator")

error_plot_66 <- sig_errors %>%
  filter( unique_id == "BL 6-6") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(operator_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Operator")


grid.arrange(mean_plot_61, error_plot_61, nrow = 2)
grid.arrange(mean_plot_62, error_plot_62, nrow = 2)
grid.arrange(mean_plot_63, error_plot_63, nrow = 2)
grid.arrange(mean_plot_64, error_plot_64, nrow = 2)
grid.arrange(mean_plot_65, error_plot_65, nrow = 2)
grid.arrange(mean_plot_66, error_plot_66, nrow = 2)



```




Some really weird stuff is going on with Allison's land 3 and 4... let's pull her out and look at that.  

```{r}
sig_errors %>% 
  filter(Operator == "Allison") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(Bullet)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  facet_grid(Round~unique_id) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6")
```


I now want to look at things due to which bullet they originated from:  
```{r}
mean_plot_61_b <- sig_errors %>% 
  filter( unique_id == "BL 6-1") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(bullet_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 1") + 
  scale_color_discrete(name = "Bullet ID")

error_plot_61_b <- sig_errors %>%
  filter( unique_id == "BL 6-1") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(bullet_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Bullet ID")
  
mean_plot_62_b <- sig_errors %>% 
  filter( unique_id == "BL 6-2") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(bullet_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 2") + 
  scale_color_discrete(name = "Bullet ID")

error_plot_62_b <- sig_errors %>%
  filter( unique_id == "BL 6-2") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(bullet_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Bullet ID")


mean_plot_63_b <- sig_errors %>% 
  filter( unique_id == "BL 6-3") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(bullet_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 3") + 
  scale_color_discrete(name = "Bullet ID")

error_plot_63_b <- sig_errors %>%
  filter( unique_id == "BL 6-3") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(bullet_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Bullet ID")


mean_plot_64_b <- sig_errors %>% 
  filter( unique_id == "BL 6-4") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(bullet_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 4") + 
  scale_color_discrete(name = "Bullet ID")

error_plot_64_b <- sig_errors %>%
  filter( unique_id == "BL 6-4") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(bullet_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Bullet ID")

mean_plot_65_b <- sig_errors %>% 
  filter( unique_id == "BL 6-5") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(bullet_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 5") + 
  scale_color_discrete(name = "Bullet ID")

error_plot_65_b <- sig_errors %>%
  filter( unique_id == "BL 6-5") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(bullet_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Bullet ID")

mean_plot_66_b <- sig_errors %>% 
  filter( unique_id == "BL 6-6") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(bullet_code)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = mean_sig), color = "black") + 
  theme_bw() + 
  #facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(x = "x location", y = "Signature Height", title = "Hamby set Barrel 6, Land 6") + 
  scale_color_discrete(name = "Bullet ID")

error_plot_66_b <- sig_errors %>%
  filter( unique_id == "BL 6-6") %>% 
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig_error, group = scan_id, color = factor(bullet_code)), alpha = 0.7) +
  geom_hline(yintercept = 0, color = "black") + 
  #facet_wrap(~unique_id, nrow = 2) + 
  theme_bw() + 
  labs(x = "x location", y = "Residual Height") + 
  scale_color_discrete(name = "Bullet ID")


grid.arrange(mean_plot_61_b, error_plot_61_b, nrow = 2)
grid.arrange(mean_plot_62_b, error_plot_62_b, nrow = 2)
grid.arrange(mean_plot_63_b, error_plot_63_b, nrow = 2)
grid.arrange(mean_plot_64_b, error_plot_64_b, nrow = 2)
grid.arrange(mean_plot_65_b, error_plot_65_b, nrow = 2)
grid.arrange(mean_plot_66_b, error_plot_66_b, nrow = 2)



```







## BARREL 5 VIZ OF SIGNATURES  


```{r}
barrel5land1 <- user_sigs %>% filter(unique_id == "BL 5-1")
barrel5land1 <- barrel5land1 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel5land1$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))


barrel5land2 <- user_sigs %>% filter(unique_id == "BL 5-2")
barrel5land2 <- barrel5land2 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel5land2$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))


barrel5land3 <- user_sigs %>% filter(unique_id == "BL 5-3")
barrel5land3 <- barrel5land3 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel5land3$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))

barrel5land4 <- user_sigs %>% filter(unique_id == "BL 5-4")
barrel5land4 <- barrel5land4 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel5land4$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))

barrel5land5 <- user_sigs %>% filter(unique_id == "BL 5-5")
barrel5land5 <- barrel5land5 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel5land5$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))

barrel5land6 <- user_sigs %>% filter(unique_id == "BL 5-6")
barrel5land6 <- barrel5land6 %>% mutate(sigs_aligned = purrr::map(sigs, .f = function(row){
  align <- sig_align(barrel5land6$sigs[[1]]$sig, row$sig)
  lands <- align$lands
  lands <- lands[!is.na(lands$sig1),]
  lands$x_aligned <- 1:(dim(lands)[1])
  lands
}))

```

```{r}
barrel5 <- rbind(barrel5land1, barrel5land2, barrel5land3, barrel5land4, barrel5land5, barrel5land6)

b5_long <- barrel5 %>% unnest(sigs_aligned)
head(b5_long)


b5_long %>% ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(Operator)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = sig1), alpha = 0.8) + 
  theme_bw() + 
  facet_wrap(~unique_id, nrow = 2) + 
  labs(title = "Hamby set Barrel 5")


b5_long %>% ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(Operator)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = sig1), alpha = 0.8) + 
  theme_bw() + 
  facet_grid(Operator~unique_id) + 
  labs(title = "Hamby set Barrel 5")


b5_long %>% ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(Machine)), alpha = 0.8) + 
  geom_line(aes(x = x_aligned, y = sig1), alpha = 0.8) + 
  theme_bw() + 
  facet_grid(Operator~unique_id) + 
  labs(title = "Hamby set Barrel 5")

```


```{r}
b5_long %>% 
  filter( unique_id == "BL 5-4") %>% 
  filter(Operator == "Carley") %>%
  ggplot() + 
  geom_line(aes(x = x_aligned, y = sig2, group = scan_id, color = factor(Operator)), alpha = 0.7) + 
  geom_line(aes(x = x_aligned, y = sig1), alpha = 0.8) + 
  theme_bw() + 
  facet_wrap(Bullet~unique_id, nrow = 2) + 
  labs(title = "Hamby set Barrel 6")
```




## Now, visualizing crosscuts on top of an image.  

To do this, we need to first grab a few full x3p files (from the server), to render locally on my machine (because image_x3p doesn't work on the server).

This first chunk of code should be commented out when working locally.  

```{r}
#filenames <- list.files("/media/Sunny/CSAFE/User comparison scans/", pattern = "*.x3p", full.names = T, recursive = T)
#barrel6_ex <- data.frame(source = filenames)
#barrel6_ex <- barrel6_ex %>% 
#  filter(str_detect(source, "Connor") == T | str_detect(source, "Anyesha") == T) %>% # grab only Connor and Anyesha's scans
#  filter(str_detect(source, "Round 4") == F)

#barrel6_ex <- barrel6_ex %>% mutate(x3p = purrr::map(as.character(source), .f = function(filename){
#  x3ptools::read_x3p(filename)
#}))


#barrel6_ex <- barrel6_ex %>% mutate(source = purrr::map_chr(as.character(source), .f = function(source){
#  strsplit(source, "//")[[1]][2]
#}))


#barrel6_ex <- barrel6_ex %>% mutate(Round = purrr::map_chr(as.character(source), .f = function(source){
#  strsplit(source, "/")[[1]][1]
#}), 
#Operator = purrr::map_chr(as.character(source), .f = function(source){
#  op <- strsplit(source, "/")[[1]][2]
#  strsplit(op, " ")[[1]][1]
#}), 
#source = factor(str_replace_all(source, ";", " -")),
#Barrel = purrr::map_chr(as.character(source), .f = function(source){
#  strsplit(source, " - ")[[1]][2]
#}), 
#Bullet = purrr::map_chr(as.character(source), .f = function(source){
#  strsplit(source, " - ")[[1]][3]
#}), 
#Land = purrr::map_chr(as.character(source), .f = function(source){
#  strsplit(source, " - ")[[1]][4]
#}), 
#Machine = purrr::map_chr(as.character(source), .f = function(source){
#  mac <- ifelse(str_detect(source, "Scan") == T, strsplit(source, " - ")[[1]][6], strsplit(source, " - ")[[1]][5]) 
#  str_replace_all(mac, " ", "")
#}), 
#Scan = purrr::map_chr(as.character(source), .f = function(source){
#  ifelse(str_detect(source, "Scan") == T, strsplit(source, " - ")[[1]][5], "Scan 1")
#}))

#barrel6_ex <- barrel6_ex %>%
#  mutate(scan_id = paste0(Barrel, "-", Land, "-", Bullet, "-", 
#                          Operator, "-", Machine, "-", Round))

#user_gt <- read_csv("../data/user_gt.csv")
#barrel6_ex <- left_join(barrel6_ex, user_gt)

#barrel6_ex <- barrel6_ex %>% filter(unique_id == "BL 6-5")


#head(barrel6_ex)

#saveRDS(barrel6_ex, "../data/barrel6_example_x3p.rda")
```


This next chunk of code should be commented out when working on the server!! 

```{r}
barrel6_x3p <- readRDS("../data/barrel6_example_x3p.rda")


## add on the correct unique_id
user_gt <- read_csv("../data/user_gt.csv")
barrel6_x3p <- left_join(barrel6_x3p, user_gt)


## grab the crosscut values
x3p_crosscuts <- readRDS("../data/user_crosscuts.rda")

x3p_crosscuts <- x3p_crosscuts %>% 
  mutate(scan_id = paste0(Barrel, "-", Land, "-", Bullet, "-", 
                          Operator, "-", Machine, "-", Round))

barrel6_x3p <- left_join(barrel6_x3p, x3p_crosscuts)
head(barrel6_x3p)

barrel6_x3p <- barrel6_x3p %>% mutate(scan_label = paste0(unique_id, "-",
                                                          Bullet, "-", Operator,"-",
                                                          Machine, "-", Round))

plot_crosscut_x3p <- function(datafile, scan_num){
  x3p <- datafile$x3p[[scan_num]]
  filename <- str_replace_all(paste0("../images/", datafile$scan_label[scan_num], ".png"), " ", "")
  x3p_line <- x3p_add_hline(x3p, yintercept = datafile$crosscut[scan_num], size = 5, color = "white")
  image_x3p(x3p_line, file = filename, size = c(3500, 1500), zoom = 0.5)
}

plot_crosscut_x3p(barrel6_x3p, 1) # we can just do this for each one! 

```


Now, we want to grab these and look at the signatures that line up with them to see if any of the drastic striae we see are due to the crosscut location.  
```{r}
barrel6_x3p <- left_join(barrel6_x3p, barrel6land5)

barrel6_long <- barrel6_x3p %>% unnest(sigs)
which.max(barrel6_long$sig)
sig_id <- barrel6_long[28313,]$scan_id

barrel6_x3p %>%
  unnest(sigs_aligned) %>%
  mutate(sig_interest = ifelse(scan_id == sig_id, 1, 0)) %>%
  ggplot() + geom_line(aes(x = x, y = sig2, group = scan_id, color = factor(Operator))) + 
  geom_line(aes(x = x, y = sig1), color = "black") + 
    theme_bw() +
  facet_grid(Round~Bullet)


# we can see there is a spike - perhaps due to crosscut being grabbed in the breakoff.
# let's add that to an x3p image
sig_breakoff <- barrel6_x3p %>% filter(scan_id == sig_id)
sig_breakoff <- x3p_add_vline(sig_breakoff$x3p[[1]], barrel6_long[28313,]$x, color = "white", size = 10)
sig_breakoff <- x3p_add_hline(sig_breakoff, barrel6_long[28313,]$y, color = "white", size = 5)
image_x3p(sig_breakoff, file = "../images/highest-crosscut-x3p.png", size = c(3500, 1500), zoom = 0.5)

```




## Next, we want to look at autocorrelations of signatures!  

```{r, echo = F, warning = F, message = F}
user_sigs <- readRDS("../data/user_meas_sigs.rda")
user_sigs <- user_sigs %>% 
  mutate(scan_id = barrellandbullet) %>% 
  select(-barrellandbullet) %>% 
  select(scan_id, sigs)
head(user_sigs)

user_gt <- read_csv("../data/user_gt.csv")
user_sigs <- full_join(user_sigs, user_gt)

head(user_sigs)


user_acf <- user_sigs %>% 
  select(scan_id, sigs, Barrel, Bullet, Operator, Machine, unique_id) %>%
  mutate(acf = purrr::map(sigs, .f = function(sigs){
    acf_obj <- acf(sigs$sig, lag.max = 200, type = "correlation", na.action = na.pass, plot = FALSE)
    data.frame(lag = acf_obj$lag[,,1], acf = acf_obj$acf[,,1])
  }))

head(user_acf)
```


```{r, echo = F, warning = F, message = F}

user_acf %>% 
  unnest(acf) %>%
  filter(str_detect(unique_id, "BL 6") == T) %>% 
  ggplot() + 
  geom_hline(yintercept = 0.95, color = "black") + 
  geom_hline(yintercept = 0, color = "grey70") + 
  geom_line(aes(x = lag, y = acf, group = scan_id, colour = factor(unique_id)), alpha = 0.6) + 
  theme_bw() + 
  facet_wrap(~unique_id, nrow = 2) + 
  scale_color_discrete(name = "Barrel-Land ID") + 
  labs(x = "Lag Value", y = "ACF Value", title = "ACF functions for repetitions on each Barrel-Land")

user_acf %>% 
  unnest(acf) %>%
  filter(str_detect(unique_id, "BL 6") == T) %>% 
  filter(lag < 50) %>%
  ggplot() + 
  geom_vline(xintercept = 5, color = "grey70") + 
  geom_hline(yintercept = 0.95, color = "black") + 
  geom_line(aes(x = lag, y = acf, group = scan_id, colour = factor(unique_id)), alpha = 0.6) + 
  theme_bw() + 
  facet_wrap(~unique_id, nrow = 2) + 
  scale_color_discrete(name = "Barrel-Land ID") + 
  labs(x = "Lag Value", y = "ACF Value", title = "ACF functions for repetitions on each Barrel-Land, lags under 50")
```



```{r, echo = F, warning = F, message = F}

user_acf %>% 
  unnest(acf) %>%
  filter(str_detect(unique_id, "BL 5") == T) %>% 
  ggplot() + 
  geom_hline(yintercept = 0.95, color = "black") + 
  geom_hline(yintercept = 0, color = "grey70") + 
  geom_line(aes(x = lag, y = acf, group = scan_id, colour = factor(unique_id)), alpha = 0.6) + 
  theme_bw() + 
  facet_wrap(~unique_id, nrow = 2) + 
  scale_color_discrete(name = "Barrel-Land ID") + 
  labs(x = "Lag Value", y = "ACF Value", title = "ACF functions for repetitions on each Barrel-Land")

user_acf %>% 
  unnest(acf) %>%
  filter(str_detect(unique_id, "BL 5") == T) %>% 
  filter(lag < 50) %>%
  ggplot() + 
  geom_vline(xintercept = 5, color = "grey70") + 
  geom_hline(yintercept = 0.95, color = "black") + 
  geom_line(aes(x = lag, y = acf, group = scan_id, colour = factor(unique_id)), alpha = 0.6) + 
  theme_bw() + 
  facet_wrap(~unique_id, nrow = 2) + 
  scale_color_discrete(name = "Barrel-Land ID") + 
  labs(x = "Lag Value", y = "ACF Value", title = "ACF functions for repetitions on each Barrel-Land, lags under 50")
```




```{r}
```




