---
title: "user-meas ground truth"
output: html_document
---


```{r packages, echo = F, warning = F, message = F}
library(tidyverse)
library(gridExtra)

```


```{r, echo = F, warning = F, message = F}
user_rfscores <- readRDS("../data/user_meas_rfscores.rda")

head(user_rfscores)

user_rfscores <- user_rfscores %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("Barrel_S1", "Land_S1", "Bullet_S1", 
                    "Operator_S1", "Machine_S1", "Round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("Barrel_S2", "Land_S2", "Bullet_S2", 
                    "Operator_S2", "Machine_S2", "Round_S2"), sep = "-")

head(user_rfscores)
user_rfscores <- user_rfscores %>% filter(Round_S1 != "Round 0" & Round_S2 != "Round 0")

```


## BARREL 6  

First, we want to find Allison's pairings with herself in each round FOR BARREL 6.  

```{r, echo = F, warning = F, message = F}
user_rfscores %>%
  filter(Operator_S1 == "Allison" & Operator_S2 == "Allison") %>% 
  filter(Barrel_S1 == "Barrel 6" & Barrel_S2 == "Barrel 6") %>% 
  filter(Bullet_S1 == "Bullet 1" & Round_S1 == "Round 1") %>% 
  ggplot(aes(x = Land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~Bullet_S2 + Round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```


Now, we will find Allison's "Bullet 1-Round 1-Land 1" pairings with Anyesha's.  


```{r, echo = F, warning = F, message = F}
user_rfscores %>%
  filter(Operator_S1 == "Allison" & Operator_S2 == "Anyesha") %>% 
  filter(Barrel_S1 == "Barrel 6" & Barrel_S2 == "Barrel 6") %>% 
  filter(Bullet_S1 == "Bullet 1" & Round_S1 == "Round 1") %>% 
  ggplot(aes(x = Land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~Bullet_S2 + Round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```



Now, we will find Allison's "Bullet 1-Round 1-Land 1" pairings with Carley's.  


```{r, echo = F, warning = F, message = F}
user_rfscores %>%
  filter(Operator_S1 == "Allison" & Operator_S2 == "Carley") %>% 
  filter(Barrel_S1 == "Barrel 6" & Barrel_S2 == "Barrel 6") %>% 
  filter(Bullet_S1 == "Bullet 1" & Round_S1 == "Round 1") %>% 
  ggplot(aes(x = Land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~Bullet_S2 + Round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

Now, we will find Allison's "Bullet 1-Round 1-Land 1" pairings with Connor's.  


```{r, echo = F, warning = F, message = F}
user_rfscores %>%
  filter(Operator_S1 == "Allison" & Operator_S2 == "Connor") %>% 
  filter(Barrel_S1 == "Barrel 6" & Barrel_S2 == "Barrel 6") %>% 
  filter(Bullet_S1 == "Bullet 1" & Round_S1 == "Round 1") %>% 
  ggplot(aes(x = Land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~Bullet_S2 + Round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

Now, we will find Allison's "Bullet 1-Round 1-Land 1" pairings with Jozef's.  


```{r, echo = F, warning = F, message = F}
user_rfscores %>%
  filter(Operator_S1 == "Allison" & Operator_S2 == "Jozef") %>% 
  filter(Barrel_S1 == "Barrel 6" & Barrel_S2 == "Barrel 6") %>% 
  filter(Bullet_S1 == "Bullet 1" & Round_S1 == "Round 1") %>% 
  ggplot(aes(x = Land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~Bullet_S2 + Round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```

Now, we will find Allison's "Bullet 1-Round 1-Land 1" pairings with Marco's.  


I subsetted these wrong. I will need to go back and re-do some of this with his scans in there.  

```{r, echo = F, warning = F, message = F}
user_rfscores %>%
  filter(Operator_S1 == "Allison" & Operator_S2 == "Marco") %>% 
  filter(Barrel_S1 == "Barrel 6" & Barrel_S2 == "Barrel 6") %>% 
  filter(Bullet_S1 == "Bullet 1" & Round_S1 == "Round 1") %>% 
  ggplot(aes(x = Land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~Bullet_S2 + Round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```



```{r, echo = F, warning = F, message = F}
user_rfscores %>%
  filter(Operator_S1 == "Allison" & Operator_S2 == "Connor") %>% 
  filter(Barrel_S1 == "Barrel 6" & Barrel_S2 == "Barrel 5") %>% 
  filter(Bullet_S1 == "Bullet 1" & Round_S1 == "Round 1") %>% 
  ggplot(aes(x = Land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~Barrel_S2 + Bullet_S2+Round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```



## Barrel 5  

Next, we want to find Allison's pairings with everybody in each round FOR BARREL 5.  

```{r, echo = F, warning = F, message = F}
user_rfscores %>%
  filter(Operator_S1 == "Allison") %>% 
  filter(Barrel_S1 == "Barrel 5" & Barrel_S2 == "Barrel 5") %>% 
  filter(Bullet_S1 == "Bullet 1") %>% 
  ggplot(aes(x = Land_S2, y = land1, fill = rfscore)) +
  geom_tile() +
  scale_fill_gradient2(low = "grey80", high = "darkorange", 
                       midpoint = .5) +
  facet_wrap(~Operator_S2 + Bullet_S2 + Round_S2) +
  #xlab("Land A") +
  #ylab("Land B") +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle =20))
```



## Making ground truth stuff.


NEED TO BE CAREFUL ABOUT THIS! DON'T WANT TO HAVE TO REDO THE ENTIRE GT DOCUMENT. 


```{r}
user_lands <- data.frame(land = unique(user_rfscores$land1))

user_lands <- user_lands %>% mutate(scan_id = land) %>% separate(land, into = c("Barrel", "Land", "Bullet", "Operator", "Machine", "Round"), sep = "-")

head(user_lands)

#old_gt <- read_csv("../data/user_gt.csv") ## without Marco's... need to add his GT in. 
#user_lands <- left_join(user_lands, old_gt)
#user_lands

write_csv(user_lands, path = "../data/user_gt.csv", col_names = TRUE) 
```

Read in ground truth Excel file and now do some stuff.  


```{r}

user_gt <- read_csv("../data/user_gt.csv")
head(user_gt)

user_mat <- matrix(NA, nrow = nrow(user_gt), ncol = nrow(user_gt))
row.names(user_mat) <- user_gt$scan_id
colnames(user_mat) <- user_gt$scan_id

for (i in 1:nrow(user_mat)){
  for(j in 1:ncol(user_mat)){
    user_mat[i,j] <- ifelse(user_gt$unique_id[i] == user_gt$unique_id[j], "Same Source", "Different Source")
  }
}


user_mat <- as.data.frame(user_mat)
user_mat$land1 <- rownames(user_mat)
user_mat <- user_mat %>% gather(1:270, key = "land2", value = "ground_truth")

head(user_mat)
user_gt <- user_gt %>% mutate(land1 = scan_id, land2 = scan_id)
user_land1 <- user_gt %>% select(land1, unique_id)
user_land2 <- user_gt %>% select(land2, unique_id)

user_rfscores <- readRDS("../data/user_meas_rfscores.rda")
user_rfscores <- right_join(user_rfscores, user_land1, by = "land1")
user_rfscores <- right_join(user_rfscores, user_land2, by = "land2")


user_results <- full_join(user_rfscores, user_mat)
user_results <- user_results %>% 
  mutate(id_S1 = land1, id_S2 = land2) %>% 
  separate(col = id_S1, 
           into = c("Barrel_S1", "Land_S1", "Bullet_S1", 
                    "Operator_S1", "Machine_S1", "Round_S1"), sep = "-") %>% 
  separate(col = id_S2, 
           into = c("Barrel_S2", "Land_S2", "Bullet_S2", 
                    "Operator_S2", "Machine_S2", "Round_S2"), sep = "-") %>%
  mutate(unique_id_S1 = unique_id.x, unique_id_S2 = unique_id.y) %>%
  select(-unique_id.x, -unique_id.y)

saveRDS(user_results, "../data/user_meas_pairwise.rda")
#head(user_results)
```



Now we're going to add ground truth for which bullet scans are coming from: 

```{r}
bullets <- readRDS("../data/user_meas_sigs.rda")

bullets <- bullets %>% filter(Round != "Round 0") 

bullets <- bullets %>% mutate(bullet_id = paste0(Operator, "-", Round, "-", Barrel, "-", Bullet))

bullets <- data.frame(bullet = unique(bullets$bullet_id))

bullets <- bullets %>% mutate(bullet_id = bullet) %>% separate(bullet, into = c("Operator", "Round", "Barrel", "Bullet"), sep = "-")

head(bullets)


#write_csv(bullets, path = "../data/user_bullets_gt.csv", col_names = TRUE) 
```


And, we want to add a blinded operator coding.  

```{r}
ops <- readRDS("../data/user_meas_sigs.rda")
ops <- data.frame(Operator = unique(ops$Operator))
#write_csv(ops, path = "../data/user_operators_blind.csv", col_names = TRUE)

```
