---
title: "user-meas_recaptures"
output: html_document
---

```{r packages, echo = F, warning = F, message = F}
library(tidyverse)
library(bulletxtrctr)
library(x3ptools)
library(gridExtra)
library(randomForest)
```

First, we want to read in the data.  

```{r}
recaptures <- readRDS("../data/user_recapture_sigs.rda") 

# can look to see how many recaptures were done for each scan
#recaptures %>% group_by(scan_id) %>% summarize(Rep = n_distinct(Scan)) 




user_gt <- read_csv("../data/user_gt.csv")
recaptures <- left_join(recaptures, user_gt)

head(recaptures)

recaptures <- recaptures %>% 
  mutate(rep_id = paste0(scan_id, "-", Scan)) %>%
  select(-grooves) %>%
  mutate(sigs = purrr::map(sigs, .f = function(sigs){
    data.frame(sigs)
  }))

## We can also look to see if the same crosscut is grabbed in each scan
recaptures %>% group_by(scan_id) %>% summarize(unique_id = unique_id[1], min_cut = min(crosscut), max_cut = max(crosscut), ncuts = n_distinct(crosscut))


recap_long <- recaptures %>% unnest(sigs)
```



First, let's just get an initial sense for recaptures with all operators, all lands.  
```{r}
recap_long %>% 
  filter(Bullet == "Bullet 1") %>% 
  ggplot() + 
  geom_line(aes(x = x, y = sig, group = rep_id, color = factor(Scan)), alpha = 0.3) + 
  theme_bw() + 
  facet_grid(Operator~unique_id) + 
  labs(title = "Hamby set Barrel 5") + 
  scale_color_discrete(name = "Repetition #")
```




Now, let's calculate MSE for each one and plot for specific scans.  

```{r}
recap_mses <- recap_long %>% 
  group_by(scan_id, x) %>% 
  mutate(rep_mean_byx = mean(sig, na.rm = T), sqerr = (sig - rep_mean_byx)^2) %>%
  ungroup() %>%
  group_by(scan_id) %>% 
  nest(x:sqerr, .key = "sigs") %>%
  mutate(recap_mse = purrr::map_dbl(sigs, .f = function(sigs){
    sqrt(sum(sigs$sqerr, na.rm = T))/length(is.na(sigs$sqerr))
  })) %>% 
  select(scan_id, recap_mse)

recap_long <- left_join(recap_long, recap_mses, by = "scan_id")
recap_long <- recap_long %>% 
  group_by(scan_id) %>% 
  mutate(Oper_MSE = paste0(Operator, " (MSE = ", format(round(recap_mse, 4),scientific = F), ")")) %>%
  ungroup()
```

```{r}

recap_long %>% 
  filter(Bullet == "Bullet 1" & unique_id == "BL 5-1") %>% 
  ggplot() + 
  geom_line(aes(x = x, y = sig, group = rep_id, color = factor(Scan)), alpha = 0.5) + 
  theme_bw() + 
  facet_wrap(~Machine+Oper_MSE, nrow = 2) + 
  labs(title = "Immediate Recaptures: Hamby set Barrel 5, Land 1 (Bullet 1)") + 
  scale_color_discrete(name = "Repetition #")

recap_long %>% 
  filter(Bullet == "Bullet 1" & unique_id == "BL 5-2") %>% 
  ggplot() + 
  geom_line(aes(x = x, y = sig, group = rep_id, color = factor(Scan)), alpha = 0.5) + 
  theme_bw() + 
  facet_wrap(~Machine+Oper_MSE, nrow = 2) + 
  labs(title = "Immediate Recaptures: Hamby set Barrel 5, Land 2 (Bullet 1)") + 
  scale_color_discrete(name = "Repetition #")


recap_long %>% 
  filter(Bullet == "Bullet 1" & unique_id == "BL 5-3") %>% 
  ggplot() + 
  geom_line(aes(x = x, y = sig, group = rep_id, color = factor(Scan)), alpha = 0.5) + 
  theme_bw() + 
  facet_wrap(~Machine+Oper_MSE, nrow = 2) + 
  labs(title = "Immediate Recaptures: Hamby set Barrel 5, Land 3 (Bullet 1)") + 
  scale_color_discrete(name = "Repetition #")

recap_long %>% 
  filter(Bullet == "Bullet 1" & unique_id == "BL 5-4") %>% 
  ggplot() + 
  geom_line(aes(x = x, y = sig, group = rep_id, color = factor(Scan)), alpha = 0.5) + 
  theme_bw() + 
  facet_wrap(~Machine+Oper_MSE, nrow = 2) + 
  labs(title = "Immediate Recaptures: Hamby set Barrel 5, Land 4 (Bullet 1)") + 
  scale_color_discrete(name = "Repetition #")

recap_long %>% 
  filter(Bullet == "Bullet 1" & unique_id == "BL 5-5") %>% 
  ggplot() + 
  geom_line(aes(x = x, y = sig, group = rep_id, color = factor(Scan)), alpha = 0.5) + 
  theme_bw() + 
  facet_wrap(~Machine+Oper_MSE, nrow = 2) + 
  labs(title = "Immediate Recaptures: Hamby set Barrel 5, Land 5 (Bullet 1)") + 
  scale_color_discrete(name = "Repetition #")

recap_long %>% 
  filter(Bullet == "Bullet 1" & unique_id == "BL 5-6") %>% 
  ggplot() + 
  geom_line(aes(x = x, y = sig, group = rep_id, color = factor(Scan)), alpha = 0.5) + 
  theme_bw() + 
  facet_wrap(~Machine+Oper_MSE, nrow = 2) + 
  labs(title = "Immediate Recaptures: Hamby set Barrel 5, Land 6 (Bullet 1)") + 
  scale_color_discrete(name = "Repetition #")
```


So, we notice that there might be an issue with Sneox2; for certain recaptures, different crosscuts are being grabbed for Anyesha and Jozef on BL 5-4. Let's see what happens when force the signatures to be calculated from the same crosscut (let's say, the minimum crosscut identified for any particular scan_id will be used for all three repetitions).  

To do this, we need to re-do the "signature" process on the server. "user-meas_sigs" will be updated with code to do this, which will be saved out as "user_recapture_force_cc.rda".  

```{r}
recap_force_cc <- readRDS("../data/user_recapture_force_cc.rda")
recap_force_cc <- recap_force_cc %>% 
  select(-sigs) %>% 
  group_by(scan_id) %>% 
  mutate(crosscut = min(crosscut)) %>%
  ungroup() %>% 
  mutate(sigs = purrr::map2(
    .x = ccdata, .y = grooves, 
    .f = function(x,y) {
      cc_get_signature(
        ccdata = x, grooves = y, span1 = 0.75, span2 = 0.03
      )
    }
  ))


```



