---
title: "pipeline exploration"
author: "Kiegan Rice"
output: html_document
---

```{r, echo = F, warning = F, message = F}
library(tidyverse)
library(bulletxtrctr)
library(x3ptools)
library(drake)
library(grooveFinder)
```

I want to test out the `drake` package and see if it can possibly integrate with the bullet pipeline.  

To do this, I am first going to test out `drake`'s `drake_plan` function, which lets you make a pipeline plan. I will test this first on a small set of signatures, and I will look at two steps: 

1. Groove ID;
2. Signature extraction.


First, let's read in some Barrel Orange data and grab a small subset of ccdata. 
```{r}
orange_ccdata <- readRDS("../../data/variability_scans/Orange_all_cc.rda")
orange_gt <- read_csv("../../data/variability_scans/orange_gt.csv")

orange_ccdata <- left_join(orange_ccdata, orange_gt)
orange_ccdata <- orange_ccdata %>% filter(unique_id == "BL O-1", bullet == "Bullet 1", operator == "Connor")
```

Let's make a `drake_plan` to take signatures, identify grooves, and extract signatures.

```{r}
plan <- drake_plan(
  data = orange_ccdata,
  data_grooves = data %>% mutate(grooves = purrr::map(ccdata, .f = cc_locate_grooves, method = "lassofull", 
               adjust = 10, return_plot = TRUE)),
  data_sigs = data_grooves %>% mutate(sigs = purrr::map2(
    .x = ccdata, .y = grooves, 
    .f = function(x, y) {
      cc_get_signature(
        ccdata = x, grooves = y, span1 = 0.75, span2 = 0.03)
    }))
)

config <- drake_config(plan)
vis_drake_graph(config)

make(plan)
```


```{r}
plan2 <- drake_plan(
  data = orange_ccdata,
  sig_data = data %>% 
    mutate(grooves = purrr::map(ccdata, .f = cc_locate_grooves, 
                                method = "lassofull", 
                                adjust = 10, return_plot = TRUE),
           sigs = purrr::map2(.x = ccdata, .y = grooves, 
                              .f = function(x, y) {
                                cc_get_signature(ccdata = x, 
                                                 grooves = y, 
                                                 span1 = 0.75, 
                                                 span2 = 0.03)})
    )
)

config2<- drake_config(plan2)
vis_drake_graph(config2)

make(plan2)
```




Let's try making a function that does what we want to our data. 


```{r}
sig_extract <- function(data, groove_method = groove_methods, span1 = span1, span2 = span2){
  sig_data <- data %>% 
    mutate(grooves = purrr::map(ccdata, .f = cc_locate_grooves, 
                                method = groove_method, 
                                adjust = 10, return_plot = TRUE),
           sigs = purrr::map2(.x = ccdata, .y = grooves, 
                              .f = function(x, y) {
                                cc_get_signature(ccdata = x, 
                                                 grooves = y, 
                                                 span1 = span1, 
                                                 span2 = span2)})
    )
  return(sig_data)
}
```

```{r}
plan3 <- drake_plan(
  data = orange_ccdata,
  sig_data = target(
    sig_extract(data, groove_method = groove_method, span1 = span1, span2 = span2),
    transform = cross(groove_method = c("lassofull", "rollapply"), span1 = c(0.5, 0.75, 1), span2 = c(0.02, 0.03, 0.04))
)
)

config3<- drake_config(plan3)
vis_drake_graph(config3)

make(plan3)
```

